### 2019-05-13 doc/bilevel/paper.tex
Drafing some modeling ideas

\subsection{TODO}

TODO: Discuss a new modeling idea here.

\subsection{TODO}

TODO: Discuss a new modeling idea here.

>>>>

\subsection{Using Set Notation}

IDEA: Declare the SubModel using arguments that define the lower-level variables whose
optimal value constrains the upper-level variables.

\begin{qlisting}
model = ConcreteModel()

model.x = Var(bounds=(1,2))
model.v = Var(bounds=(1,2))
model.y = Var(bounds=(1,2))

model.o = Objective(expr=model.x + model.v + model.y)
model.c = Constraint(expr=model.x + model.v >= 1.5)

model.sub = SubModel(fixed=[model.x, model.v], y=model.y)

# NOTE - model.sub.y is implicitly defined
model.sub.w = Var(bounds=(-1,1))

model.sub.o = Objective(expr=model.x + model.sub.w, sense=maximize)
model.sub.c = Constraint(expr=model.sub.y + model.sub.w <= 2.5)
\end{qlisting}

\noindent PROS
\begin{itemize}
\item More explicit than pyomo.bilevel
\end{itemize}
CONS
\begin{itemize}
\item Users may not appreciate this difference and use model.y instead of model.sub.y.  Can we robustly catch errors when that happens?
\item May not be able to capture complex relationships between upper- and lower-level variables
\item May not be useful for defining pessimistic relationships.
\end{itemize}

\subsection{Using Set Notation}

IDEA:  What if the SubModel declaration defined a set, which can be explicitly used to
define a constraint (similar to~(\ref{eqn:bilevel})?

TODO ...
